Spatial Analysis: Design-Based vs Model-Based

### 2021-01-29 draft.Rnw
minor updates

\begin{enumerate}
  \item There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. From what we have seen, these comparisons are between spatial model-based approaches and independent random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison 
  \item Misspecification
  \item Finite AND infinite populations
  \item Centered around the pragmatic questions practitioners will be faced with
  \item Provide reliable software

@@

\subsection*{Potential Journals}

@@

__MH Thoughts:__ I'd like to keep this section manageable. Perhaps we start with the following examples \begin{itemize}
  \item simulate via correct model (model outperforms sampling)
   \item simulate via slightly misspecified model (model still outperforms sampling)
  \item simulate via very misspecified model (sampling outperforms model)
  \item simulate via extremely misspecified model (e.g. counts with lots of zeroes and a lot of overdispersion) (neither does well)
\end{itemize}

>>>>

\begin{enumerate}
  \item Spatial Design-Based vs Spatial Model-Based: There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. From what we have seen, these comparisons are between spatial model-based approaches and independent random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison: We feel that literature in this area has considered scenarios that are more well-suited for the model-based scenario. For example, if you simulate a Gaussian erorr with an exponential covariance and then then compare design-based estimates to model-based estimates assuming an exponential covariance, of course the model-based approach will outperform design-based approaches. And these are the types of comparisons in the literature, which find model-based approaches generally yield more precise variance estiamtes. A challenge lies in creating a comparison scenario that is reasonable and intuitive. One this to consider would be exploring the comparison after estimating a misspecified covariance function using model-based approaches. 
  \item Finite AND infinite populations: Literature in the area focuses specifically on finite populations or infinite populations; we want to discuss both in detail.
  \item Pragmatic Focus: We see papers in this area tend to be fairly technical. We want the focus to be less on details, more on discussing the pragmatic questions practitioners will be faced with. For example, a thorough discussion of benefits and drawbacks of each method written for practicioners is warranted.
  \item Provide reliable software

@@

\subsection*{Potential Journals}
\begin{itemize}
  \item Ecological Applications
  \item Methods in Ecology and Evolution
  \item Journal of Applied Ecology
  \item Environmetrics
  \item Environmental and Ecological Statistics
\end{itemize}

@@

We would like to keep this section manageable. Perhaps we start with the following examples 
\begin{itemize}
  \item simulate via correct model (model outperforms sampling)
  \item simulate via slightly misspecified model (model still outperforms sampling)
  \item simulate via very misspecified model (sampling outperforms model)
  \item simulate via extremely misspecified model (e.g. counts with lots of zeroes and a lot of overdispersion) (neither does well)
\end{itemize}

### 2021-01-29 draft.tex
minor updates

>>>>

We would like to keep this section manageable. Perhaps we start with the following examples 
\begin{itemize}
  \item simulate via correct model (model outperforms sampling)
  \item simulate via slightly misspecified model (model still outperforms sampling)
  \item simulate via very misspecified model (sampling outperforms model)
  \item simulate via extremely misspecified model (e.g. counts with lots of zeroes and a lot of overdispersion) (neither does well)
\end{itemize}
